## Practical Machine Learning
### Assignment
-- Author: hpschu --

```{r}
library(caret)
```


```{r}
# Download data:
download.file('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv', method = 'curl', destfile = 'training.csv')
download.file('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv', method = 'curl', destfile = 'testing.csv')

training <- as.data.frame(read.table('training.csv', sep=",", header = T))
testing <- as.data.frame(read.table('testing.csv', sep=",", header = T))
summary(training)
summary(testing)
Ntr <- dim(training)[1]
Nte <- dim(testing)[1]
```

The X-variable seems to work as an index variable and is thus removed from the training- and test sets. Additionally, max_roll_belt, max_picth_belt, min_roll_belt, min_pitch_belt, amplitude_roll_belt, amplitude_pitch_belt, and var_total_accel_belt had a vast amount of missing variables. These variables were also removed.

```{r}
training <- subset(as.data.frame(training), select=-c(1, 10:16))

View(training)


nearZeroVar(rbind(training[, -dim(training)[2]], testing[,-dim(testing)[2]]), saveMetrics = T)
zeroVar <- nearZeroVar(rbind(training[, -dim(training)[2]], testing[,-dim(testing)[2]]))

training <- training[,-zeroVar]
testing <- testing[,-zeroVar]
View(training)
View(testing)
```

